---
title: "simpleRegress"
author: "put your name here"
date: "Fall 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
#adjust factors to be factors
bears$SEX<- as.factor(bears$SEX)
bears$MONTH<- as.factor(bears$MONTH)
```

## Model LENGTH ~ NECK  this is an example 

We are going to compute regression models finding one regression model that does the best job in preventing the bear length,and neck size , age, head width and head length and order them from most accurate from most to least.


```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```
the adjusted r square that is the largest and best.The neck size is 0.7476

## Compare all models that predict LENGTH other than NECK. Then order them from worst to best by its value of Adjusted-Rsquared (bigger is better), or by RSE (residual standard error) where smaller is better. 

```{r}
simp <- lm(LENGTH~HEADLEN,data=bears)
plot(LENGTH~HEADLEN,data=bears)
abline(simp)
summary.lm(simp)
```
The adjusted r square for head length is 0.8434.

```{r}
simp <- lm(LENGTH~HEADWTH,data=bears)
plot(LENGTH~HEADWTH,data=bears)
abline(simp)
summary.lm(simp)
```
the adjusted r square for HEADWTH is  0.5321 .

```{r}
simp <- lm(LENGTH~AGE,data=bears)
plot(LENGTH~AGE,data=bears)
abline(simp)
summary.lm(simp)
```
the adjusted r square for AGE is 0.5073

```{r}
simp <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(simp)
summary.lm(simp)
```
The r squared for CHEST is  0.7869 .

```{r}
simp <- lm(LENGTH~WEIGHT,data=bears)
plot(LENGTH~WEIGHT,data=bears)
abline(simp)
summary.lm(simp)
```
THE adjusted R SQUARE FOR WEIGHT IS 0.7423 

### Disscusion Conclusion 
Considering the adjusted r square for all of these considering which is the adjusted r square is the best shown from the graphs above.Consulting head size opposed to the other is best  

  
Age          .05073.       

Headwith     .05321          

Weight       .07423          

Neck         .07476            

Chest        .07869                


Head Length   0.8434


In conclusion, the lowest R square, 0.5073 for the age, is the best model out of the 6.  

